Differentially Private Bayesian Inference

### 2018-04-13 main.tex
update

\section{Bayesian Inference Based on Beta-Bernoulli Distribution}
\label{sec_bayesInfer}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$.

In our inference algorithm, we take a Dirichlet distribution as $prior$, $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_3)$.

\section{Algorithm Setting up}
\label{sec_setup}

For now, we already have a prior distribution $prior$, an observed data set $x$.

@@

\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 S(x)})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 S(x)})},
\end{equation*}
where the sensitivity in mechanism is smooth sensitivity $S(x)$, calculated by:
\begin{equation*}
S_{\beta}(x) = \max(\Delta_{l}u(x), \max_{y \neq x; y \in D^{n}}(\Delta_{l}u(y)\cdot e^{-\beta d(x,y)})),
\end{equation*}
where $\beta = \beta(\epsilon, \delta)$. In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.

>>>>

\section{Bayesian Inference Based on Beta-Bernoulli Distribution}
\label{sec_bayesInfer}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

In our inference algorithm, we take a Dirichlet distribution as $prior$, $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$. Columns of the data set is corresponding to the number of parameters ($m$) in Dirichlet distribution. The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the number of $1$ at the column $i$ in observed data set.

In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$. Then we have only one column take value from $\{0,1\}$. THe posterior is computed as $(\alpha + n_1, \beta + n_0))$, where $n_1$ is the number of $1$ in the data set and $n_0$ is the number of $0$ in the data set.

\section{Algorithm Setting up}
\label{sec_setup}
For now, we already have a prior distribution $prior$, an observed data set $x$.

@@

\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 S(x)})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 S(x)})},
\end{equation*}
where the sensitivity in mechanism is smooth sensitivity $S(x)$\cite{nissim2007smooth}, calculated by:
\begin{equation*}
S_{\beta}(x) = \max(\Delta_{l}u(x), \max_{y \neq x; y \in D^{n}}(\Delta_{l}u(y)\cdot e^{-\beta d(x,y)})),
\end{equation*}
where $\beta = \beta(\epsilon, \delta)$. In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.
